\vspace*{\fill}
\begin{centering}
\section{Search I: First search for diboson resonances at 13 TeV}
When the LHC started its Run II data taking period in summer 2015, it would be the first time ever for a particle collider to produce collisions with center-of-mass energies of 13 TeV. The high-energy physics community was at cross roads. The Higgs boson for which the LHC was designed to find, had been discovered at the end of the previous data taking era.We were stuck with a Standard Model that we knew was, in the best case, in need of extensions and in the worst case an effective theory valid only in a certain region of phenomena phase space. The search program in Run II would therefore be oriented around two main efforts: Precision measurements of the newly discovered Higgs boson and searches for Beyond Standard Model physics.\newline\newline
I started my PhD four months before the first 13 TeV collisions took place and was faced with the following questions:
What was the most interesting search that could be done on a short time scale (to be presented 6 months after first collisions, at the CERN end-of-year Jamboree), that would be manageable for a student with no experience to perform alone and that would be robust enough incase the never-before-validated 13 TeV Monte Carlo would fail? \newline\newline
Every year in high-energy physics has its hype: In 2018, this was most certainly leptoquarks (driven by a dimuon excess around 30 GeV), in 2016 and 2017 is was diphoton resonances ( with  $>3\sigma$ excesses observed both in ATLAS and in CMS). And in 2015 during the 13 TeV LHC start-up, it was all about diboson resonances in the all-hadronic final state.\newline\newline
The choice was clear: My first analysis would be a search for diboson resonances in the boosted dijet final state. With a background model based on a smooth fit to data in the signal region, eliminating the need for accurate QCD MC predictions, this was a simple one-background only (QCD) analysis, feasible for a first-year PhD student to take on alone and finalize within a year. Despite its straightforwardness, due to observed 8 TeV excesses it was in addition considered a high-profile, high-impact analysis.
\newline\newline
This introduces Search I: First search for diboson resonances at 13 TeV.
\end{centering}

\vspace*{\fill}\newpage
\input{searchI.tex}

\vspace*{\fill}\newpage
\vspace*{\fill}
\section{Search II: Developing a new pileup resistant and infrared safe tagger}
With the first 13 TeV search for dibosons published and the awareness that the pileup in 2016 would double with respect to what was observed in 2015, the development of new and more robust taggers was the main focus of 2016. 
\vspace*{\fill}\newpage
\input{searchII.tex}

\vspace*{\fill}\newpage
\vspace*{\fill}
\section{Search III: A novel multi-dimensional search}
After two successful analyses of 13 TeV data, no excess had been observed in the all-hadronic VV channels.
\vspace*{\fill}\newpage
\input{searchIII.tex}



