\section{The Standard Model Lagrangian}
Everything this thesis is built on, has its roots in the Standard Model. The Standard Model of particle physics (SM) addresses the question \emph{What is matter made of?} on the smallest possible scale. It maps the fundamental constituents of the universe together through the forces that bind them, hoping to provide a complete picture of the laws of nature. The Standard Model is formulated as a quantum field theory, where the fundamental particles are fermions who interact with one another through the exchange of bosons. These interaction comes in three forms, each mediated by three different bosons: The electromagnetic force, mediated through photons, the weak force, mediated through W and Z bosons, and the strong force, mediated by gluons. How the fundamental particles interact, also defines which properties they exhibit. In addition, the Standard Model includes a field very different from the others, the Higgs field. The Higgs field is felt by both fermions and bosons and is what gives all particles their mass.\newline
One thing the Standard Model fails to incorporate, is the force of gravity. This shortcoming is one of the main motivations for looking for alternative models beyond the Standard Model (BSM), which is the main topic of this thesis.

\subsection{Fundamental particles: Quarks and leptons}
It appears that all matter in the universe can be described by a very small collection of fundamental particles, six leptons and six quarks. These are collectively called fermions and are, as far as we can tell, truly elementary (not composed of any other particles).
Leptons are particles with integer or zero electric charge (defined in units of electron charge). They come in three flavours, or generations, and their mass increases with generation. Each generation of leptons consists of two particles: one charged lepton and one neutrally charged particle denoted \emph{neutrino ($\nu$)}. The three generations can be arranged in a doublet structure, and are as follows
\begin{equation}
\label{eqn:lepton_flavor_doublets}
\begin{pmatrix} e       \\ \nu_e      \end{pmatrix} \qquad
\begin{pmatrix} \mu     \\ \nu_{\mu}  \end{pmatrix} \qquad
\begin{pmatrix} \tau    \\ \nu_{\tau} \end{pmatrix}
\end{equation}
The leptons come in two states; positively charged and negatively charged, where charged is defined in unit of electron charge $e$. The base state is negatively charged, $e^{-}$, $\mu^{-}$, and $\tau^{-}$,  whereas the positively charged leptons,  $e^{+}$, $\mu^{+}$, and $\tau^{+}$ are considered their anti-particles states.
Each lepton generation is assigned its own quantum number $L$ which must be conserved after any process. A summary of the lepton properties is listed in Table~\ref{table:theory:lepprop}.
\begin{table}[h!]
\begin{center}
\begin{tabular}{|c|c|c| c c c|}
\hline
Lepton        & Mass           & Charge & $L_{e}$ & $L_{\mu}$ & $L_{\tau}$ \\
\hline
$e^{-}$      & $0.5 \mbox{ MeV}$   & $e$ & 1       & 0         & 0 \\
$\mu^{-}$    & $106 \mbox{ MeV}$   & $e$ & 0       & 1         & 0 \\
$\tau^{-}$   & $1777 \mbox{ MeV}$  & $e$ & 0       & 0         & 1 \\
\hline
$\nu_{e}$    & $< 3 \mbox{ eV}$       & $0$    & 1       & 0         & 0 \\
$\nu_{\mu}$  & $< 0.19 \mbox{ MeV}$   & $0$    & 0       & 1         & 0 \\
$\nu_{\tau}$ & $< 18.2 \mbox{ MeV}$   & $0$    & 0       & 0         & 1 \\
\hline
\end{tabular}
\end{center}
\caption{Lepton Properties}
\label{table:theory:lepprop}
\end{table}
Leptons interact with one another through the \emph{electromagnetic and weak force}, which will be explained in more detailed in Section~\ref{sec:theory:ew}.\newline
The other six fundamental matter particles are the \emph{quarks}. They are distinguished from the leptons in that they interact with one another through the \emph{strong force}, described in Section~\ref{sec:theory:qcd}. This force binds the quarks together to form baryons (like protons and neutrons) or mesons (like pions), and in addition keeps the quarks from being observed as free particles (they are only visible through their baryon/meson bound states) Also organized in three generations, the six quarks are called \textit{up}, \textit{down}, \textit{charm}, \textit{strange}, \textit{top} and \textit{bottom}, and are organized in flavor doublets as follow
\begin{equation}
\label{eqn:quark_flavor_doublets}
\begin{pmatrix} u \\ d \end{pmatrix} \qquad
\begin{pmatrix} c \\ s \end{pmatrix} \qquad
\begin{pmatrix} t \\ b \end{pmatrix}
\end{equation}
Each quark comes with a fractional charge of $-\frac{1}{3}$ (u, c and t) and $\frac{2}{3}$ (d, s and b) of one electron charge. As with the leptons, they also come with distinct particles of opposite charge, anti-quarks. As mentioned above, quarks can interact with one another through the strong force. However, they also interact through the weak and electro-magnetic forces.
Some of the quark properties are listed in Table~\ref{table:theory:quarkprop}.
\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|}%c|}
\hline
Quark & Mass & Charge \\% & Properties \\
\hline
u & $1-5 \mbox{ MeV}$         & $\phantom{-}\frac{2}{3} e$  \\%& $I_{z} = \frac{1}{2}$ \\
d & $3-9 \mbox{ MeV}$         & $-\frac{1}{3} e$            \\%& $I_{z} = -\frac{1}{2}$ \\
c & $1.15-1.35 \mbox{ GeV}$   & $\phantom{-}\frac{2}{3} e$  \\%& Charm = +1 \\
s & $75-170 \mbox{ MeV}$      & $-\frac{1}{3}e$             \\%& Strangeness = -1 \\
t & $\approx 174 \mbox{ GeV}$ & $\phantom{-}\frac{2}{3} e$  \\%& Top = +1 \\
b & $4.0-4.4 \mbox{ GeV}$     & $-\frac{1}{3} e$            \\%& Bottom = -1 \\
\hline
\end{tabular}
\end{center}
\caption{Quark Properties}
\label{table:theory:quarkprop}
\end{table}
These 12 fermions, together with their corresponding anti-particles, represent the fundamental particles of the Universe and build up all matter we see around us. We categorize them through which forces they interact with, the fundamental forces, which also has a large impact on the particles properties.
There are four fundamental forces that we know of: Gravity, electromagnetism, the weak force and the strong force. Gravity is so weak compared to the other forces, that it can safely be ignored in the energy domain we probe in this thesis. 
All particles which are electrically charged, interact through the electromagnetic force. In our tables above, that includes the charged leptons ($e$, $\mu$ and $\tau$) and all of the quarks. These interactions are governed by the laws of Quantum Electro Dynamics (QED). All of the fermions, now also including the neutral neutrinos, feel the weak force and undergo weak interactions. The weak force is mediated through vector bosons (W and Z) and it is only due to the fact that the quarks feel this force, that we can look for vector bosons decaying into quarks in this thesis. Finally, we have the strong force. Only quarks interact via the strong force, and it is that interaction that makes the quarks so fundamentally different from electrons and neutrinos. The strong force keeps us from observing quarks as free particles, and keep them in bound states referred to as \emph{hadrons}. Their interaction is governed by the laws of Quantum Chromodynamics (QCD). All of these interactions can be represented in one common framework, the Standard Model.
\subsection{The Standard Model Fields}
\label{sec:theory:ew}
\subsection{The Higgs Mechanism}
\subsection{Quantum Chromodynamics}
\label{sec:theory:qcd}
\section{Beyond Standard Model Physics}
\subsection{The hierarchy problem and the gravitational force}
\subsection{Theories of New Physics}
\subsubsection{Warped extra dimensions}
\label{sec:theory:wed}
\subsubsection{Compositeness}
\subsection{Heavy Vector Triplet formalism}
\label{sec:theory:hvt}
	